WTCIII-Figures

### 2015-07-02 markdown/WTC3_figures.Rmd
finished smooth plot CIs of several figures.  Calculated r2 for main figure linear fits.  minor adjsutments to plots
made plots fit on a smaller window for later ease

#### <u>Figures</u>
```{r par, fig.width=6, fig.height=6}
source("master_scripts/par.R")
```  
Figure 1. Local light environment for sun and shade leaves for each gas exchange campaign. Means and standard errors represent 1m integrated PPFD (n=5), measured with a ceptometer, at the canopy height of each selected leaf.

```{r acicurves, fig.width=8, fig.height=10}
source("master_scripts/aci_vcmaxnitro.R")
```  
Figure2. Predicted photosynthetic CO~2~ response (ACi) curves for sun and shade leaves at elevated and ambient temperature treatments. ACi curves were developed at 25°C and at saturating light (1800 $\mu$mols m^-1^ s^-1^)(a). The relationship between Vc~max~ and leaf nitrogen~area~ for sun and shade leaves at elevated and ambient temperature treatments (b). ACi curves were taken once on well watered trees before the initiation of the drought treatment.

```{r wateruse, fig.width=8, fig.height=10}
source("master_scripts/wateruse.R")
```  
Figure 3. Response of instantaneous water use efficiency (ITE) to leaf vapor pressure deficit (VPD) for sun leaves and shade leaves at both low and high light (a) and the relationship between leaf $\delta$^13^C and leaf nitrogen~area~ for sun and shade leaves at elevated and ambient temperature treatments. For (a) VPD is the leaf to air pressure difference inside the gas exchange cuvette and lines represent predictions from the optimal ITE model with a g1 value for each leaf type and treatment.

```{r gmgs, fig.width=8, fig.height=10}
source("master_scripts/gmgs.R")
```  
Figure 4. The response of leaf photosynthesis rates to stomatal conductance (a) and mesophyll conductance (b) for sun leaves and shade leaves at both low and high light with elevated and ambient temperature treatments.  Dashed lines represent 95% confidence intervals from a general additive model with a smoothing factor of 5.  The response of shade leaf physiology to high light was recorded once both photosynthesis and stomatal conductance were stable in the gas exchange leaf cuvette (ca. 25min).

```{r cicc, fig.width=10, fig.height=6}
source("master_scripts/cicc_bar.R")
```  
Figure 5. The average intercellular CO~2~ concentraion (a), CO~2~ concentration in the chloroplasts (b) and CO~2~ drawdown from substomatal cavities to sites of carboxylation of sun leaves and shade leaves at both low and hight light with standard errors.

```{r barplots, fig.width=10, fig.height=6}
source("master_scripts/physiology_barplots.R")
```  
The average stomatal conductance (a), mesophyll conductance (b) and photosynthesis (c) between sun leavse and  shade leaves at both low and high light with standard errors.

#### <u>Supplementary Figures</u>
```{r gmparN, fig.width=8, fig.height=10}
source("master_scripts/gm_par_nitro.R")
``` 
Figure S1. The relationship between mesophyll conductance, leaf PPFD and leaf nitrogen.

```{r gmT, fig.width=6, fig.height=6}
source("master_scripts/gm_temp.R")
``` 
Figure S2. Response of mesophyll conductance to leaf temperature  for sun and shade leaves at elevated and ambient temperature treatments. For (a) and (b) lines represent 95% confidence intervals generated with bootstrapping methods (n=999) from mixed effect linear model equations with chamber as a random effect.

>>>>

#### <u>Figures</u>
```{r par, fig.width=6, fig.height=6}
source("master_scripts/par.R")
```  
Figure 1. Local light environment for sun and shade leaves for each gas exchange campaign. Means with standard errors represent 1 m integrated PPFD (n=5), measured with a ceptometer, at the canopy height of each selected leaf.

```{r acicurves, fig.width=6, fig.height=8}
source("master_scripts/aci_vcmaxnitro.R")
```  
Figure2. (a) Photosynthetic CO~2~ response (ACi) curves for sun and shade leaves at elevated (ET) and ambient (AT) temperature treatments. ACi curves were developed once for all trees, before the initiation of the drought treatment, at 25°C and at saturating light (1800 $\mu$mols m^-1^ s^-1^). (b) The relationship between Vc~max~ and mean leaf nitrogen~area~ for each chamber, including sun leaves and shade leaves at low light. For (b) the dashed line represents the significant linear model fit for all leaves with a marginal and conditional r^2^ of 0.28 and 0.35, respectively.

```{r wateruse, fig.width=6, fig.height=8}
source("master_scripts/wateruse.R")
```  
Figure 3. (a) Response of instantaneous water use efficiency (ITE) to leaf vapor pressure deficit (VPD) for sun leaves and shade leaves at both low and high light with elevated and ambient temperature treatments. (b) The relationship between leaf $\delta$^13^C and leaf nitrogen~area~ for sun leaves and shade leaves at low light. For (a) VPD is the leaf to air pressure difference inside the gas exchange cuvette and lines represent predictions from the optimal ITE model with a g1 value for each leaf type and treatment. For (b) the dashed line represents the significant linear model fit for all leaves with a marginal and conditional r^2^ of 0.41 and 0.45, respectively.

```{r Agmgs, fig.width=6, fig.height=8}
source("master_scripts/Agmgs.R")
```  
Figure 4. The response of leaf photosynthesis rates to stomatal conductance (a) and mesophyll conductance (b) for sun leaves and shade leaves at both low and high light with elevated and ambient temperature treatments.  The response of shade leaf physiology to high light was recorded once both photosynthesis and stomatal conductance were stable in the gas exchange leaf cuvette (ca. 25min). Lines represent either smoothed regressions from a generalized additive model fit (a) or linear model fits (b). Grey areas are approximately 95% confidence intervals from the mean.

```{r barplots, fig.width=10, fig.height=5}
source("master_scripts/physiology_barplots.R")
```  
The mean stomatal conductance (a), mesophyll conductance (b) and photosynthesis rate (c) of sun leaves and shade leaves at both low and high light with standard errors.

```{r cicc, fig.width=10, fig.height=5}
source("master_scripts/cicc_bar.R")
```  
Figure 5. The mean intercellular CO~2~ concentration (a), CO~2~ concentration in the chloroplasts (b) and CO~2~ drawdown from substomatal cavities to sites of carboxylation of sun leaves and shade leaves at both low and high light with standard errors.

#### <u>Supplementary Figures</u>
```{r gmgs, fig.width=6, fig.height=6}
source("master_scripts/gmgs.R")
``` 
Figure S1. Mesophyll conductance as a function of stomatal conductance for sun leaves and shade leaves at both low and high light with elevated and ambient temperature treatments. The dashed line is the 1:1 relationship.

```{r gmT, fig.width=6, fig.height=6}
source("master_scripts/gm_temp.R")
``` 
Figure S2. Response of mesophyll conductance to leaf temperature for sun and shade leaves at elevated and ambient temperature treatments. Solid lines represent linear model fits and grey areas are approximately 95% confidence intervals from the mean.

```{r gmparN, fig.width=6, fig.height=10}
source("master_scripts/gm_par_nitro.R")
``` 
Figure S3. (a) Mesophyll conductance as a function of leaf nitrogen~area~ for sun leaves and shade leaves at low light with elevated and ambient temperature treatments. (b) Mesophyll conductance has a function of PPFD for all leaf types. (c) Leaf nitrogen~area~ as a function of PPFD for all leaf types. Dashed line represents linear model fits.
